---
title: "Symb_Choice_ddPCR"
author: "Shayle Matsuda"
date: "12/7/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
This is data from the Symbiont Choice 2018 experiment conducted at AIMS in 2018 and 2019. 
Data: ddPCR

```{r setup chunk, setup, warning=FALSE, message=FALSE, fig.align='center'}
require("knitr")

knitr::opts_knit$set(root.dir = normalizePath("~/Desktop/Symb_choice/Symbiont Choice 2018"))
```

```{r}
rm(list=ls()) # Clear workspace
```
## Background

Authors: S. Matsuda, L. Chakravarti, R. Cunning, M.van Oppen, R. Gates
Symbiont choice experiment tests the uptake of cultured Symbiodiniaceae alone and as a mixture in A. tenuis larvae at ambient (27C) and two elevated (30C and 31C) temperatures over the course of 2 weeks. Sampling was on days 3, 7 and 14. 

```{r}
# Set up workspace
setwd("~/Desktop/Symb_choice/Symbiont Choice 2018")

library(plyr)
library(dplyr)
library(ggplot2)
library("gridExtra") #arrange plots for output
```


Load in ddPCR data with Threshold set in QuantaSoft Analysis
```{r}
#Read in plate data

Plate1<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE1_20190424_threshold.csv")
Plate2<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE2_20190429_threshold.csv")
Plate3<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE3_20190426_threshold.csv")
Plate3B<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE3B_20190426_threshold.csv")
Plate3 <- rbind(Plate3,Plate3B) # merge plate 3 and 3b for metadata
Plate4<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE4_20190427_threshold.csv")
Plate5<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE5_20190428_threshold.csv")
Plate6<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE6_20190428_threshold.csv")
Plate7<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE7_20190429_threshold.csv")
Plate8<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE8_20190501_threshold.csv")
Plate9<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE9_20190501_threshold.csv")
Plate10<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE10_20190501_threshold.csv")
Plate11<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE11_20190502_threshold.csv")
Plate12<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE12_20190502_threshold.csv")
Plate13<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE13_20190503_threshold.csv")
Plate14<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE14_20190503_threshold.csv")
Plate15<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE15_20190507_threshold.csv")
Plate16<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE16_20190508_threshold.csv")
Plate17<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE17_20190509_threshold.csv")
Plate18<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE18_20190509_threshold.csv")
Plate19<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE19_20190509_threshold.csv")
Plate20<- read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/SHAYLE_PLATE20_20190510_threshold.csv")

# read in metadata by plate (some samples are duplicate names, which is why)
meta1 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate1_meta.csv")
meta2 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate2_meta.csv")
meta3 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate3_meta.csv")
meta4 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate4_meta.csv")
meta5 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate5_meta.csv")
meta6 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate6_meta.csv")
meta7 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate7_meta.csv")
meta8 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate8_meta.csv")
meta9 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate9_meta.csv")
meta10 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate10_meta.csv")
meta11 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate11_meta.csv")
meta12 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate12_meta.csv")
meta13 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate13_meta.csv")
meta14 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate14_meta.csv")
meta15 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate15_meta.csv")
meta16 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate16_meta.csv")
meta17 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate17_meta.csv")
meta18 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate18_meta.csv")
meta19 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate19_meta.csv")
meta20 <-read.csv("~/Desktop/Symb_choice/Symbiont Choice 2018/ddPCR_thresholdData/Plate20_meta.csv")

# merge each plates meta with plate
P1<-merge(Plate1, meta1, by="Well")
P2<-merge(Plate2, meta2, by="Well")
P3<-merge(Plate3, meta3, by="Well")
P4<-merge(Plate4, meta4, by="Well")
P5<-merge(Plate5, meta5, by="Well")
P6<-merge(Plate6, meta6, by="Well")
P7<-merge(Plate7, meta7, by="Well")
P8<-merge(Plate8, meta8, by="Well")
P9<-merge(Plate9, meta9, by="Well")
P10<-merge(Plate10, meta10, by="Well")
P11<-merge(Plate11, meta11, by="Well")
P12<-merge(Plate12, meta12, by="Well")
P13<-merge(Plate13, meta13, by="Well")
P14<-merge(Plate14, meta14, by="Well")
P15<-merge(Plate15, meta15, by="Well")
P16<-merge(Plate16, meta16, by="Well")
P17<-merge(Plate17, meta17, by="Well")
P18<-merge(Plate18, meta18, by="Well")
P19<-merge(Plate19, meta19, by="Well")
P20<-merge(Plate20, meta20, by="Well")

#merge all plates
dData1 <- rbind(P1, P2, P3, P4, P5, P6, P7, P8, P9, P10, P11, P12, P13, P14, P15, P16, P17, P18, P19, P20)

 #write.csv(dData, "dData.csv")
#only keep columns you need (Sample, Target, Conc(copies/µL), Copies/20ulWell, Accepted Droplets, Positives, Negatives, Threshold1, metadata)

dData<-dData1[,c(1,2:4,11,16:18,31,66 ,68:79)]
dData$Conc.copies.µL.<-as.numeric(dData$Conc.copies.µL.)
dData$Temp<-as.character(dData$Temp)
dData$Day<-as.numeric(dData$Day)

```

Calculate concentration per larvae <- is this correct
```{r}
#figure out how much DNA is in 20ul of PCR rxn (xulDNA in 25ulrxn)
dData$DNA.20ul<-(dData$ul.DNA*20)/25

# use copies/1ul pcr to calculate how many copies are in 1 larvae. (copies/1ul PCR)*(20ul PCR/yUL DNA)*(20uLDNA/1 larvae)
dData$copies.larvae<-(dData$Conc.copies.µL.)*(20/dData$DNA.20ul)*20


############ Something is acting off in the ALLs below, try using conc.20ul to see if that fixes it
testData<-dData
testData$copies.1ultest<-(dData$Copies.20µLWell/20)
```

Calculate copy number ***** When you do this, add this step here (will not significantly change results)
```{r}
#CopyNumber<-subset(dData, Info=="CopyNumber")
#write.csv(CopyNumber,"CopyNumber_20191208.csv")
```


```{r}
# divide copies by copy number per clade
dData$copyNum[dData$Primer=="C1"]<-24
dData$copyNum[dData$Primer=="D1"]<-7
dData$copyNum[dData$Primer=="F1"]<-39
dData$copyNum[dData$Primer=="G3"]<-247

# calc number of Sym cells in larvae
dData$cells.larvae<-dData$copies.larvae/dData$copyNum
  dData<-dData[!(dData$Info=="NTC"),]
```

Subset data for diff analyses
```{r}
#subset only copynumber calc samples
CopyNumber<-subset(dData, Info=="CopyNumber")

#subset only FalsePositives
FalsePos<-subset(dData, Info=="CONTROL")
write.csv(FalsePos, "FalsePos.csv")

#subset Samples
sData<-subset(dData, Info=="ALL"|Info=="C1"|Info=="D1"|Info=="F1"|Info=="G3")
```

Decide where your cut off for positive droplets is. Standard is 10,000. You should push down to 900. 
```{r}
sData1<-subset(sData, Accepted.Droplets>9000)# remove samples with less than 9000 droplets (we lose 60 samples)

```

Subset for each Infection trial (C1, D1, F1, G3, ALL)
```{r}
C1<-subset(sData1, Info=="C1")
D1<-subset(sData1, Info=="D1")
F1<-subset(sData1, Info=="F1")
G3<-subset(sData1, Info=="G3")
ALL<-subset(sData1, Info=="ALL")
```

C1 single infection
```{r}
C1_mean <- ddply(C1, c("Day", "Temp"), summarise, #summarize cell counts
                 N    = length(cells.larvae[!is.na(cells.larvae)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(cells.larvae, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(cells.larvae, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(cells.larvae, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
C1_mean #display table
```
Plot C1 single infection
```{r}
C1_plot<-ggplot(data=C1_mean, aes(x=Day, y=mean, group = Temp, color=Temp)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Temp), size=4, show.legend = T)+
  geom_line(aes(color=Temp))+
  scale_color_manual(values=c("dodgerblue3", "orange", "darkred"))+
  xlab("Days") + #Label the X Axis
  ylim(-10,400) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Cells/Larvae"))) +
  ggtitle("C1 average infection per larvae")+
  theme(plot.title = element_text(size=20, face = "italic"));C1_plot
```

D1 single infection
```{r}
D1_mean <- ddply(D1, c("Day", "Temp"), summarise, #summarize cell counts
                 N    = length(cells.larvae[!is.na(cells.larvae)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(cells.larvae, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(cells.larvae, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(cells.larvae, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
D1_mean #display table
```
Plot D1 single infection
```{r}
D1_plot<-ggplot(data=D1_mean, aes(x=Day, y=mean, group = Temp, color=Temp)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Temp), size=4, show.legend = T)+
  geom_line(aes(color=Temp))+
  scale_color_manual(values=c("dodgerblue3", "orange", "darkred"))+
  xlab("Days") + #Label the X Axis
  ylim(-10, 400) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Cells/Larvae"))) +
  ggtitle("D1 average infection per larvae")+
  theme(plot.title = element_text(size=20, face = "italic"));D1_plot
```

F1 single infection
```{r}
F1_mean <- ddply(F1, c("Day", "Temp"), summarise, #summarize cell counts
                 N    = length(cells.larvae[!is.na(cells.larvae)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(cells.larvae, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(cells.larvae, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(cells.larvae, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
F1_mean #display table
```
Plot F1 single infection
```{r}
F1_plot<-ggplot(data=F1_mean, aes(x=Day, y=mean, group = Temp, color=Temp)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Temp), size=4, show.legend = T)+
  geom_line(aes(color=Temp))+
  scale_color_manual(values=c("dodgerblue3", "orange", "darkred"))+
  xlab("Days") + #Label the X Axis
  ylim(-10, 400) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Cells/Larvae"))) +
  ggtitle("F1 average infection per larvae")+
  theme(plot.title = element_text(size=20, face = "italic"));F1_plot
```

G3 single infection
```{r}
G3_mean <- ddply(C1, c("Day", "Temp"), summarise, #summarize cell counts
                 N    = length(cells.larvae[!is.na(cells.larvae)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(cells.larvae, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(cells.larvae, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(cells.larvae, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
G3_mean #display table
```
Plot G3 single infection
```{r}
G3_plot<-ggplot(data=G3_mean, aes(x=Day, y=mean, group = Temp, color=Temp)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Temp), size=4, show.legend = T)+
  geom_line(aes(color=Temp))+
  scale_color_manual(values=c("dodgerblue3", "orange", "darkred"))+
  xlab("Days") + #Label the X Axis
  ylim(-10, 400) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Cells/Larvae"))) +
  ggtitle("G3 average infection per larvae")+
  theme(plot.title = element_text(size=20, face = "italic"));G3_plot
```

Plot all four SINGLE INFECTION together:
```{r}

C1_plot<-C1_plot+ theme(legend.position = "none") #remove legend
D1_plot<-D1_plot+ theme(legend.position = "none") #remove legend
F1_plot<-F1_plot+ theme(legend.position = "none") #remove legend
G3_plot<-G3_plot+ theme(legend.position = "none") #remove legend

grid.arrange(C1_plot, D1_plot, F1_plot,G3_plot, nrow = 2)
```

#Multi-infection

A*************FIGURE OUT HOW TO SUBSET THE ALLS FOR ONLY LARVAE ("ALL.NUMBER"" COLUMN) THAT HAVE OVER 9000 DROPLETS FOR EACH OF THE FOUR PRIMERS***************** THen do that here before any of the stuff below. (you did in excel before by hand)

Subset by Temp treatments
```{r}
ALL_27<-subset(ALL, Temp==27)
ALL_30<-subset(ALL, Temp==30)
ALL_31<-subset(ALL, Temp==31)
```

Ambient 27C
```{r}
ALL_27_mean <- ddply(ALL_27, c("Day", "Temp","Primer"), summarise, #summarize cell counts
                 N    = length(cells.larvae[!is.na(cells.larvae)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(cells.larvae, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(cells.larvae, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(cells.larvae, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
ALL_27_mean #display table
```

Plot All 27 single infection
```{r}
ALL_27_plot<-ggplot(data=ALL_27_mean, aes(x=Day, y=mean, group = Primer, color=Primer)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Primer), size=4, show.legend = T)+
  geom_line(aes(color=Primer))+
  scale_color_manual(values=c("dodgerblue3", "orange", "darkred","green"))+
  xlab("Days") + #Label the X Axis
  #ylim(-10, 5000) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Cells/Larvae"))) +
  ggtitle("Multi-infection average infection per larvae")+
  theme(plot.title = element_text(size=20, face = "italic"));ALL_27_plot
```

High 30C
```{r}
ALL_30_mean <- ddply(ALL_30, c("Day", "Temp","Primer"), summarise, #summarize cell counts
                 N    = length(cells.larvae[!is.na(cells.larvae)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(cells.larvae, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(cells.larvae, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(cells.larvae, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
ALL_30_mean #display table
```

Plot All 30 single infection
```{r}
ALL_30_plot<-ggplot(data=ALL_30_mean, aes(x=Day, y=mean, group = Primer, color=Primer)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Primer), size=4, show.legend = T)+
  geom_line(aes(color=Primer))+
  scale_color_manual(values=c("dodgerblue3", "orange", "darkred","green"))+
  xlab("Days") + #Label the X Axis
  #ylim(-10, 5000) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Cells/Larvae"))) +
  ggtitle("Multi-infection average infection per larvae; 30C")+
  theme(plot.title = element_text(size=20, face = "italic"));ALL_30_plot
```

High 31C
```{r}
ALL_31_mean <- ddply(ALL_31, c("Day", "Temp","Primer"), summarise, #summarize cell counts
                 N    = length(cells.larvae[!is.na(cells.larvae)]), #calculate the length of the data frame, excluding NA’s *this part is important*
                 mean = mean(cells.larvae, na.rm=TRUE), #calculate mean of response variable, removing NA's
                 sd   = sd(cells.larvae, na.rm=TRUE), #calculate standard deviation
                 se   = sd / sqrt(N), #calculate standard error
                 max = max(cells.larvae, na.rm=TRUE) #calculate max, could also calculate min () if desired
)
ALL_31_mean #display table
```

Plot All 31 single infection
```{r}
ALL_31_plot<-ggplot(data=ALL_31_mean, aes(x=Day, y=mean, group = Primer, color=Primer)) +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=0.1, show.legend = T)+
  geom_point(aes(color=Primer), size=4, show.legend = T)+
  geom_line(aes(color=Primer))+
  scale_color_manual(values=c("dodgerblue3", "orange", "darkred","green"))+
  xlab("Days") + #Label the X Axis
  #ylim(-10, 5000) + #set Y limits
  theme_bw() + #Set the background color
  theme(axis.line = element_line(color = 'black'), #Set the axes color
        axis.title=element_text(size=14,face="bold"), #Set axis format
        panel.border = element_blank(), #Set the border
        panel.grid.major = element_blank(), #Set the major gridlines
        panel.grid.minor = element_blank(), #Set the minor gridlines
        text = element_text(size=18),  # set element text
        plot.background =element_blank(), #Set the plot background
        legend.key = element_blank()) + #Set plot legend key
  ylab(expression(paste("Cells/Larvae"))) +
  ggtitle("Multi-infection average infection per larvae")+
  theme(plot.title = element_text(size=20, face = "italic"));ALL_31_plot
```

Plot all three ALL temps together:
```{r}
ALL_27_plot<-ALL_27_plot+ theme(legend.position = "none") #remove legend
ALL_30_plot<-ALL_30_plot+ theme(legend.position = "none") #remove legend
ALL_31_plot<-ALL_31_plot+ theme(legend.position = "none") #remove legend  Note that at 31 most larvae are dead.

grid.arrange(ALL_27_plot, ALL_30_plot, ALL_31_plot, nrow = 1)
```

#Plot infection of individual larvae

27C Day 3
```{r}
ALL_27_Day3<-subset(ALL_27, Day==3)
ALL_27_Day3plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_27_Day3,
                           stat="identity");ALL_27_Day3plot
```
#Plot infection of individual larvae
27C Day 7
```{r}
ALL_27_Day7<-subset(ALL_27, Day==7)
ALL_27_Day7plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_27_Day7,
                           stat="identity");ALL_27_Day7plot
```

#Plot infection of individual larvae
27C Day 14
```{r}
ALL_27_Day14<-subset(ALL_27, Day==14)
ALL_27_Day14plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_27_Day14,
                           stat="identity");ALL_27_Day14plot
```

Plot all three ALL 27C days together:
```{r}
ALL_27_Day3plot<-ALL_27_Day3plot+ theme(legend.position = "none") #remove legend
ALL_27_Day7plot<-ALL_27_Day7plot+ theme(legend.position = "none") #remove legend
#ALL_27_Day14plot<-ALL_27_Day14plot+ theme(legend.position = "none") #remove legend  Note that at 31 most larvae are dead.

grid.arrange(ALL_27_Day3plot, ALL_27_Day7plot, ALL_27_Day14plot, nrow = 1)
```

30C Day 3
```{r}
ALL_30_Day3<-subset(ALL_30, Day==3)
ALL_30_Day3plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_30_Day3,
                           stat="identity");ALL_30_Day3plot
```
#Plot infection of individual larvae
30C Day 7
```{r}
ALL_30_Day7<-subset(ALL_30, Day==7)
ALL_30_Day7plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_30_Day7,
                           stat="identity");ALL_30_Day7plot
```

#Plot infection of individual larvae
30C Day 14
```{r}
ALL_30_Day14<-subset(ALL_30, Day==14)
ALL_30_Day14plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_30_Day14,
                           stat="identity");ALL_30_Day14plot
```

Plot all three ALL 30C days together:
```{r}
ALL_30_Day3plot<-ALL_30_Day3plot+ theme(legend.position = "none") #remove legend
ALL_30_Day7plot<-ALL_30_Day7plot+ theme(legend.position = "none") #remove legend
#ALL_30_Day14plot<-ALL_30_Day14plot+ theme(legend.position = "none") #remove legend  Note that at 31 most larvae are dead.

grid.arrange(ALL_30_Day3plot, ALL_30_Day7plot, ALL_30_Day14plot, nrow = 1)
```


31C Day 3
```{r}
ALL_31_Day3<-subset(ALL_31, Day==3)
ALL_31_Day3plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_31_Day3,
                           stat="identity");ALL_31_Day3plot
```
#Plot infection of individual larvae
31C Day 7
```{r}
ALL_31_Day7<-subset(ALL_31, Day==7)
ALL_31_Day7plot<-ggplot() + 
  geom_bar(aes(y = cells.larvae, x = ALL.number, fill = Primer), data = ALL_31_Day7,
                           stat="identity");ALL_31_Day7plot
```

Plot all three ALL 31C days together:
```{r}
ALL_31_Day3plot<-ALL_31_Day3plot+ theme(legend.position = "none") #remove legend
#ALL_31_Day7plot<-ALL_31_Day7plot+ theme(legend.position = "none") #remove legend

grid.arrange(ALL_31_Day3plot, ALL_31_Day7plot, nrow = 1)
```

